Compact orbitals enable low-cost linear-scaling \emph{ab initio} molecular dynamics for weakly-interacting systems

### 2018-05-27 JCP/manuscript.tex
Modified Figure 2 + Updated Refs
Made Figure 2 Longer, and added the two requested references to the .bib file.
minor corrections before merge

The inherently stochastic approach presented here does not aim to produce fully time-reversible dynamics for atomic nuclei. 
Nevertheless, it is capable to reproduce correct dynamical properties of a system as long as $\gamma$ is set to a small value and  partially optimized ALMOs remain close to the ground state resulting in $\Delta \ll \gamma$. 
An alternative approach to performing microcanonical MO-based LS AIMD would be to combine ALMO DFT with the extended Lagrangian method described in Ref.~\onlinecite{Niklasson2008} that has been shown to conserve the total energy in DM-based simulations~\cite{Cawkwell2012}.

>>>>

The inherently stochastic approach presented here does not aim to produce fully time-reversible dynamics for atomic nuclei. 
Nevertheless, it is capable to reproduce correct dynamical properties of a system as long as $\gamma$ is set to a small value and  partially optimized ALMOs remain close to the ground state resulting in $\Delta \ll \gamma$. 
An alternative approach to performing microcanonical MO-based LS AIMD would be to combine ALMO DFT with the extended Lagrangian method described in Ref.~\onlinecite{Niklasson2008}. This method has been shown to conserve the total energy in LS DM-based AIMD simulations~\cite{Cawkwell2012}.
